State Results

### 2023-07-09 reports/county_figures.Rmd
update figures

if(filter_versions) {
  county <- county %>%
    filter(version %in% c("v3", "v5", "v6", "v7")) 
}

@@

date_labels_all <-  unique(heatmap_dat$date_lab)
date_labels <- date_labels_all[seq(2, length(date_labels),by=2)]

heatmap_dat %>%
  ggplot(aes(x=fct_reorder(date_lab, date),
             y = fct_reorder(name,m),
             fill =exp_cases_median/positive)) +
  geom_tile() +
 # scale_x_discrete(breaks=breaks_date, labels = breaks_date)  +
  viridis::scale_fill_viridis(option="rocket", direction=-1) +
  labs(x="",
       y= "",
       fill = "Ratio of Estimated Infections\nto Observed Infections",
       title = "Ratio of Median Estimated Infections to Observed Infections\nfor Counties in Massachusetts") +
  theme_c() +
  theme(axis.text.x = element_text(size=14, angle=90),
        axis.text.y = element_text(size = 17),
        axis.title = element_text(size=16),
        legend.title = element_text(face="bold", size=18),
        plot.title =element_text(size=22),
        plot.subtitle = element_text(size=20)) +
  scale_x_discrete(breaks = date_labels_all, labels=date_labels)

@@

###########################################################################
# plot relationship between ratio of estimated cases to observed 
# against testing rate 
###########################################################################
county %>%
  ggplot(aes(x=total/population, y = exp_cases_median/positive)) +
  geom_point(alpha=.03, size=.9) +
  facet_wrap(~vlabel,
               labeller= labeller(vlabel =as_labeller(TeX, default=label_parsed))) +
  theme_c(axis.text.x = element_text(size =9),
          axis.title = element_text(size=16) ) +
  theme(strip.text.x = element_text(size=11, color="white")) +
  scale_y_continuous(n.breaks=10) +
  geom_hline(yintercept=1, linetype=2,color="darkred", alpha=.8, linewidth=.5) +
  labs(y = "Ratio of Estimated Infections to Observed Infections",
       x = "Testing Rate",
       subtitle = "All Time Intervals for Counties in Massachusetts",
       title = "Relationship Between Testing Rate and\nRatio of Estimated Infections to Observed Infections")+
  scale_x_continuous(limits=c(lb,.3), n.breaks=4)

@@

>>>>

FILT_VERSIONS <- c("v3", "v5", "v6", "v7")

if(filter_versions) {
  county <- county %>%
    filter(version %in% FILT_VERSIONS) 
}

@@

date_labels_all <-  unique(heatmap_dat$date_lab)
date_labels <- date_labels_all
date_labels[seq(1, length(date_labels_all),by=2)] <- ""

#date_labels <- date_labels_all[seq(1, length(date_labels_all),by=2)]

heatmap_dat %>%
  ggplot(aes(x=fct_reorder(date_lab, date),
             y = fct_reorder(name,m),
             fill =exp_cases_median/positive)) +
  geom_tile() +
 # scale_x_discrete(breaks=breaks_date, labels = breaks_date)  +
  viridis::scale_fill_viridis(option="rocket", direction=-1) +
  labs(x="",
       y= "",
       fill = "Ratio of Estimated Infections\nto Observed Infections",
       title = "Ratio of Median Estimated Infections to Observed Infections\nfor Counties in Massachusetts") +
  theme_c() +
  theme(axis.text.x = element_text(size=13, angle=90),
        axis.text.y = element_text(size = 17),
        axis.title = element_text(size=16),
        legend.title = element_text(face="bold", size=18),
        plot.title =element_text(size=22),
        plot.subtitle = element_text(size=20)) +
  scale_x_discrete(breaks = date_labels_all, labels=date_labels)

@@

###########################################################################
# plot relationship between ratio of estimated cases to observed 
# against testing rate 
###########################################################################
county %>%
  ggplot(aes(x=total/population, y = exp_cases_median/positive)) +
  geom_point(alpha=.03, size=.9) +
  facet_wrap(~vlabel,
               labeller= labeller(vlabel =as_labeller(TeX, default=label_parsed))) +
  theme_c(axis.text.x = element_text(size =9),
          axis.title = element_text(size=16) ) +
  theme(strip.text.x = element_text(size=11, color="white")) +
  scale_y_continuous(n.breaks=10) +
  geom_hline(yintercept=1, linetype=2,color="darkred", alpha=.8, linewidth=.5) +
  labs(y = "Ratio of Estimated Infections to Observed Infections",
       x = "Testing Rate",
       subtitle = "All Time Intervals for Counties in Massachusetts",
       title = "Relationship Between Testing Rate and\nRatio of Estimated Infections to Observed Infections")+
  scale_x_continuous(limits=c(lb,.3), n.breaks=6)

@@

# Table Showing Covidestim Coverage

versions <- tibble(
  version = c( "v3", "v5", "v6", "v7"),
  vlabel = factor(
    c(  "$P(S_1|$untested) Centered at Survey Value"  ,
    "$\\beta$ Centered at Survey Value",
    "$P(S_1|$untested) and $\\beta$ Centered at Survey Values",
     "Priors Do Not Vary by State or Date"
    ),
    levels =   c(  "$P(S_1|$untested) Centered at Survey Value"  ,
    "$\\beta$ Centered at Survey Value",
    "$P(S_1|$untested) and $\\beta$ Centered at Survey Values",
     "Priors Do Not Vary by State or Date"
    ))
)
```

```{r load-state}

state <- tar_read(state_v1, 
                   store =targets_dir) %>% 
  bind_rows(
    tar_read(state_v2,
             store =targets_dir)
  ) %>%
   bind_rows(
    tar_read(state_v3, 
             store =targets_dir)
  ) %>%
   bind_rows(
    tar_read(state_v4, 
             store =targets_dir)
   )%>%
   bind_rows(
    tar_read(state_v5,
             store =targets_dir)
  )%>%
   bind_rows(
    tar_read(state_v6,
             store =targets_dir)
  ) %>%
   bind_rows(
    tar_read(state_v7,
             store =targets_dir)
  )

covidestim_state <- tar_read(covidestim_biweekly_state,
                        store =targets_dir)

state_covidestim <- state %>%
  inner_join(covidestim_state, relationship="many-to-many",
             by = c('fips'='state', 'biweek'='biweek')) %>%
  distinct() %>%
  filter(version %in% FILT_VERSIONS)

county_covidestim <- county %>%
  inner_join(covidestim, relationship = "many-to-many") %>%
  select(-date) %>%
  distinct()

get_coverage <- function(df, geo_scale) {
  df %>%
    mutate(in_interval = case_when(
    exp_cases_lb <= infections & 
      infections <= exp_cases_ub ~ "Contained in Interval",
    exp_cases_lb  > infections  ~ "Below Interval",
    exp_cases_ub < infections ~ "Above Interval"
  ) ) %>%
  group_by(version, in_interval) %>%
  summarize(n=n()) %>%
  group_by(version) %>%
  mutate(total = sum(n)) %>%
  ungroup() %>%
  mutate(prop = n/total) %>%
  select(version, prop, in_interval) %>%
  pivot_wider(names_from = in_interval, values_from=prop, names_prefix="Percent ") %>%
  mutate(across(contains("Percent"), ~.x*100 )) %>%
 # mutate(across(contains("Percent"), ~paste0(round(.x,3),"%")))
  left_join(versions) %>%
    mutate(`Geographic Scale` = geo_scale) %>%
  select( `Geographic Scale`,
         Implementation = vlabel, 
          `Percent Below Interval`,
         `Percent Contained in Interval`,
           `Percent Above Interval`)
}

county_coverage <- county_covidestim %>% get_coverage(geo_scale="County")
saveRDS(county_coverage, here("figures/table_data/county_coverage.RDS"))

state_coverage <- state_covidestim %>% get_coverage(geo_scale="State")
saveRDS(state_coverage, here("figures/table_data/state_coverage.RDS"))

\@ref(table:coverage) is

county_coverage %>%
  bind_rows(state_coverage) %>%
  group_by(`Geographic Scale`) %>%
  arrange(desc(`Percent Contained in Interval`),
          .by_group=TRUE) %>%
  ungroup() %>%
  select(-`Geographic Scale`) %>%
  kbl(caption = "\\label{table:coverage}Coverage of Covidestim Medians",
      booktabs=TRUE,  
      escape=FALSE,
      digits=3) %>%
  kable_styling() %>%
  group_rows(start_row=1, end_row =4, group_label= "County") %>%
  group_rows(start_row=5, end_row =8, group_label= "State")

```{r,eval=FALSE}

county_coverage <- county_covidestim %>%
 mutate(in_interval = case_when(
    exp_cases_lb <= infections & 
      infections <= exp_cases_ub ~ "Contained in Interval",
    exp_cases_lb  > infections  ~ "Below Interval",
    exp_cases_ub < infections ~ "Above Interval"
  ) ) %>%
  group_by(version, in_interval) %>%
  summarize(n=n()) %>%
  group_by(version) %>%
  mutate(total = sum(n)) %>%
  ungroup() %>%
  mutate(prop = n/total) %>%
  select(version, prop, in_interval) %>%
  pivot_wider(names_from = in_interval, values_from=prop, names_prefix="Percent ") %>%
  mutate(across(contains("Percent"), ~.x*100 )) %>%
 # mutate(across(contains("Percent"), ~paste0(round(.x,3),"%")))
  left_join(versions) %>%
  select( # `Geographic Scale`,
         Implementation = vlabel, 
         `Percent Above Interval`,
         `Percent Contained in Interval`,
          `Percent Below Interval`)

### 2023-07-09 reports/state_figures.Rmd
update figures

all_versions <- state_res %>% 
  group_by(state) %>%
  summarize(state_n=n_distinct(version)) %>%
  filter(state_n == max(state_n)) %>%
  pull(state)
```

@@

### Original Priors versus CTIS Priors (that do not vary)

state_res %>%
  filter(version %in% c("v1","v7") & state %in% sample(unique(.$state),15)) %>%
   ggplot() +
  geom_ribbon(aes(x = date, 
             ymin = exp_cases_lb,
             ymax = exp_cases_ub,
             fill=vlabel),
             alpha = .6,
             show.legend=FALSE,
             ) +
  facet_wrap(~name, 
             labeller=labeller(vlabel =as_labeller(
               TeX, default=label_parsed),
               nrow=3),
             scales="free_y") +
  scale_y_continuous(labels = comma) +
  scale_x_date(date_breaks = "3 months", 
               date_labels = "%b %Y") +
  theme_c(
          legend.position = "top",
          ) +
  viridis::scale_fill_viridis(option="magma", begin=.1,end=.9, discrete=TRUE)  +
  labs(x="",
       y = "Estimated Infections",
       title = "Simulation Intervals Over Time",
       subtitle = "By State")

@@

```{r,eval=save_figures, fig.height=10,fig.width=12}

>>>>

all_versions <- state_res %>% 
  group_by(state) %>%
  summarize(state_n=n_distinct(version)) %>%
  filter(state_n == max(state_n)) %>%
  pull(state)

@@

### Wu *et al.*'s Priors versus CTIS Priors (that do not vary)

```{r, fig.width=14,fig.height=9}

colors_labs <- state_res %>%
  filter(version %in% c("v1","v7")) %>%
  pull(vlabel) %>% unique()

state_res %>%
  filter(version %in% c("v1","v7") & state %in% sample(unique(.$state),15)) %>%
   ggplot() +
  geom_ribbon(aes(x = date, 
             ymin = exp_cases_lb,
             ymax = exp_cases_ub,
             fill=vlabel),
             alpha = .6
             ) +
  facet_wrap(~name, 
             labeller=labeller(vlabel =as_labeller(
               TeX, default=label_parsed),
               nrow=3),
             scales="free_y") +
  scale_y_continuous(labels = comma) +
  scale_x_date(date_breaks = "3 months", 
               date_labels = "%b %Y") +
  theme_c(
          legend.position = "top",
          ) +
  viridis::scale_fill_viridis(option="magma", begin=.1,end=.9, discrete=TRUE,
                              breaks =(colors_labs),
                              labels=TeX(as.character(colors_labs)))  +
  labs(x="",
       y = "Estimated Infections",
       title = "Simulation Intervals Over Time",
       subtitle = "By State",
       fill = "")

@@

```{r,eval=save_figures, fig.height=10,fig.width=14}
